\documentclass[10pt]{article}
\usepackage[margin=2.5em]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\linespread{0.8}

\titleformat{\section}
  {\normalfont\fontsize{12}{15}\bfseries}{\thesection}{1em}{}

\begin{document}

\pagenumbering{gobble}

\centerline{\LARGE \textbf{\textsc{Patrik Ackland}}}

\begin{center}
  \url{http://www.csc.kth.se/~packland} \\
  \vspace{0.3em}
  \begin{tabular}{l r}
    packland@cs.uw.edu&(206) 890-8507
  \end{tabular} \\
  \vspace{0.3em}
  \textbf{Graduating in June 2017.}
\end{center}

\section*{Education}
\vspace{0.1em}
\hline
\vspace{0.3em}
\noindent\textbf{University of Washington}, Seattle, WA\hfill\textit{2015--2016}\\
\indent-- \textbf{Exchange}, Computer Science, GPA: 3.8/4.0\\
\indent-- Highly competitive selection process. Only one student from my university admitted every year.\\

\noindent\textbf{KTH Royal Institute of Technology}, Stockholm, Sweden\hfill\textit{2012--2017}\\
\indent-- \textbf{BS/MS}, Computer Science, GPA: 4.8/5.0\\

\section*{Experience}
\vspace{0.1em}
\hline
\vspace{0.3em}
\noindent\textbf{Yelp, Software Engineering Intern}, San Francisco, CA\hfill\textit{Summer 2016}\\
\indent-- \\
\indent Skills:--\\

\noindent\textbf{Scania, Software Engineering Intern}, Södertälje, Sweden\hfill\textit{Summer 2015}\\
\indent-- Continued developing project from the previous year.\\
\indent-- Implemented requests from teams within the company.\\
\indent-- Added several new features including digital envelope cryptography using open-ssl.\\
\indent Skills: C, C++, Cryptography, MATLAB. \\

\noindent\textbf{KTH Royal Institute of Technology, Teaching Assistant}, Stockholm, Sweden\hfill\textit{2013--2015}\\
\indent-- Teaching programming and algorithms to 15 computer-science students.\\
\indent-- Grading weekly assignments and supervising month-long project at the end of the course. \\
\indent Skills: Java, Go, Theoretical computer science. \\

\noindent\textbf{Scania, Software Engineering Intern}, Södertälje, Sweden\hfill\textit{Summer 2014}\\
\indent-- Developed software for logging road and vehicle data in trucks.\\
\indent-- The software replaced commercial software saving thousands of dollars.\\
\indent Skills: C, C\#, Agile development.\\

\section*{Projects\hfill {\normalsize\normalfont  More projects at \url{http://www.csc.kth.se/~packland}}}
\vspace{0.1em}
\hline
\vspace{0.3em}
\noindent\textbf{Compiler in Scala}, project course\hfill\textit{Scala}\\
\indent-- Compiles a subset of Scala to JVM bytecode.\\
\indent-- Handwritten lexer, parser, name analyzer and type checker.\\
\indent-- Supports Java-like generics through type erasure.\\
\indent-- Received an A, the highest grade.\\

\noindent\textbf{Chromium}, open source web browser\hfill \textit{C++} \\
\indent-- Currently working on good-first-bugs. \\
\indent-- Looking to work on more complex issues as I get more experience.\\

\noindent\textbf{Picture-of-pictures}, personal project\hfill \textit{Ruby, JavaScript} \\
\indent-- Replaces each pixel in an image with an image whose dominant color is closest to the color of the pixel.\\
\indent-- Choosing better data structures reduced running time by 90\%. \\

\section*{Programming}
\vspace{0.1em}
\hline
\vspace{0.3em}
\indent Main: \textbf{Java (6 years)}, \textbf{Android (2 years)}, \textbf{C++ (2 years)}\hspace{2em} Other: Python, JavaScript, Scala, Ruby, C\#, Go\\

\section*{Leadership Experience}
\vspace{0.1em}
\hline
\vspace{0.3em}
\noindent\textbf{Head of Sponsor, International Reception, KTH}\hfill\textit{2014--2014} \\
\indent-- Spent six months together with 13 other students planning the international reception.\\
\indent-- Welcomed over 2000 students during four arrival days and planned a month of activities. \\

\noindent\textbf{President of the Education Committee, KTH}\hfill\textit{2013--2014} \\
\indent-- Nominated by my predecessor because of my involvement the previous year.\\
\indent-- Meetings with students and faculty to discuss courses and the computer science department.\\

\section*{Awards}
\vspace{0.1em}
\hline
\vspace{0.3em}
\textbf{Henrik Göransson Sandviken Scholarship}\hfill\textit{2015}\\
\indent-- Awarded scholarship for academic achievements at KTH Royal Institute of Technology.\\
\indent-- Selection based on GPA. Awarded to 90 students in total from all majors at the university.\\

\section*{Other}
\vspace{0.1em}
\hline
\vspace{0.3em}
\indent Clubs: UW photography club, education committee, business-relations group, international reception. \\
\indent Interests: photography, guitar.
\end{document}
