\documentclass[10pt]{article}

\usepackage[margin=2.3em]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\usepackage{courier}
\usepackage[]{parskip}

\linespread{0.8}

\titlespacing
  {\section}
  {0pt}
  {\parskip}
  {-\parskip}

\titleformat
  {\section}
  {\normalfont\fontsize{12}{15}\bfseries}
  {\thesection}
  {0.2em}
  {}
  [\hline\vspace{0.2em}]

\newcommand
  {\itemtitle}
  [3]
  {\noindent\textbf{#1}, #2\hfill\textit{#3}\\}

\begin{document}

\pagenumbering{gobble}

\centerline{\LARGE \textbf{\textsc{Patrik Ackland}}}

\begin{center}
  \url{http://packlnd.github.io}\\
  \vspace{0.15em}
  \url{https://github.com/packlnd}\\
  \vspace{0.15em}
  \begin{tabular}{l r}
    patrikackland@gmail.com&+46 734 199 318
  \end{tabular} \\
  \vspace{0.15em}
  \textbf{Graduating in June 2017.}
\end{center}
\section*{Education}
\itemtitle{KTH Royal Institute of Technology}{Stockholm, Sweden}{2015--(2017)}
-- \textbf{MS}, Computer Science.

\itemtitle{University of Washington}{Seattle, WA}{2015--2016}
-- \textbf{Exchange}, Computer Science.\\
-- Highly competitive selection process. Only one student from my university admitted every year.

\itemtitle{KTH Royal Institute of Technology}{Stockholm, Sweden}{2012--2015}
-- \textbf{BS}, Computer Science, GPA: 4.8/5.0.

\section*{Experience}
\itemtitle{Yelp, Software Engineering Intern}{San Francisco, CA}{Summer 2016}
-- Full-stack development on the Yelp Reservations diner growth team.\\
-- Helped launch \texttt{www.yelp.com/reservations/\{biz-alias\}}.\\
-- Won \emph{Most useful project} at Yelps internal hackathon.\\
Skills: Python, JavaScript.

\itemtitle{Scania, Software Engineering Intern}{Södertälje, Sweden}{Summer 2015}
-- Continued developing project from the previous year.\\
-- Added several new features including digital envelope cryptography using open-ssl.\\
Skills: C, C++, Cryptography, MATLAB.

\itemtitle{KTH Royal Institute of Technology, Teaching Assistant}{Stockholm, Sweden}{2013--2015}
-- Teaching programming and algorithms to 15 computer-science students.\\
-- Grading weekly assignments and supervising month-long project at the end of the course. \\
 Skills: Java, Go, Theoretical computer science.

\itemtitle{Scania, Software Engineering Intern}{Södertälje, Sweden}{Summer 2014}
-- Developed software for logging road and vehicle data in trucks.\\
-- The software replaced commercial software saving thousands of dollars.\\
 Skills: C, C\#, Agile development.

\section*{Projects\hfill {\normalsize\normalfont 15+ projects at \url{https://github.com/packlnd}}}
\itemtitle{Compiler in Scala}{project course}{Scala}
-- Compiles a subset of Scala to JVM bytecode. Supports Java-like generics through type erasure.\\
-- Handwritten lexer, parser, name analyzer and type checker.

\itemtitle{Lamp controller}{personal project}{Electrical Engineering, Python, Swift}
-- Controls my floor lamp through an iPhone app and a Raspberry Pi web server.\\
-- The Raspberry Pi is soldered to a wall socket remote which controls the lamp.

\itemtitle{TourIt, HackTech 2016}{virtual reality project from hackathon}{Python, Virtual Reality, Unity}
-- AirBnB-like virtual reality tour guide website.\\
-- Uses Oculus Rift and 360 degrees photosphere images to make it seem like you are there.

\itemtitle{Picture-of-pictures}{personal project}{Ruby, JavaScript}
-- Replaces each pixel in an image with an image whose dominant color is closest to the color of the pixel.\\
-- Choosing better data structures reduced running time by 90\%.

\section*{Programming}
 Main: \textbf{Java (7 years)}, \textbf{C++ (3 years)}, \textbf{Python (2 years)}\hspace{2em} Other: Android, JavaScript, Scala, Ruby, C\#, Go

\section*{Leadership Experience}
\noindent\textbf{Head of Sponsor, International Reception, KTH}\hfill\textit{2014--2014} \\
-- Spent six months together with 13 other students planning the international reception.\\
-- Welcomed over 2000 students during four arrival days and planned a month of activities.

\noindent\textbf{President of the Education Committee, KTH}\hfill\textit{2013--2014} \\
-- Nominated by my predecessor because of my involvement the previous year.\\
-- Meetings with students and faculty to discuss computer science courses.

\section*{Awards}
\textbf{Henrik Göransson Sandviken Scholarship}\hfill\textit{2015}\\
-- Awarded scholarship for academic achievements at KTH Royal Institute of Technology.\\
-- Selection based on GPA. Awarded to 90 students in total from all majors at the university.
\end{document}
